10th International Satisfiability Modulo Theories Competition (SMT-COMP 2015): Rules and Procedures

### 2015-06-16 rules/rules15.tex
(exit) is mandatory for the application track.
Post-processor renamed.

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.0, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB~v2 commands in
which:
%
\begin{enumerate}
\item In the main track, there may be a (single) \akey{set-option
  :print-success ...} command.  Note that {\tt success} outputs are
  ignored by the post-processor used by the
  competition.\footnote{SMT-LIB~2.0 requires that a solver produce a
    \texttt{success} answer after each \akey{set-logic},
    \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
    (among others), unless the option \akey{:print-success} is set to
    false.  Ignoring the \texttt{success} outputs allows for
    submitting fully SMT-LIB~2.0 compliant solvers without the need
    for a wrapper script, while still allowing entrants of previous
    competitions to run without changes.}
\item In the application track, the \akey{:print-success} option may
  not be disabled; the application track executor will send an initial
  $\akey{set-option :print-success true}$ command to the solver.
\item The (single) $\akey{set-logic}$ command setting the benchmark's
  logic is the first command after any $\akey{set-option}$ commands.
\item The script next optionally contains (any number of)
  $\akey{set-info}$ commands, which may be ignored by the
  solver. Benchmarks will likely have some of the following
  \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)},
  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}, and
  \akey{(set-info :status ...)}.
\item In the main track, there is exactly one $\akey{check-sat}$
  command, following possibly several $\akey{assert}$ commands.
\item In the application track, there are one or more \akey{check-sat}
  commands, each preceded by one or more \akey{assert} commands.
  There may also be zero or more \akey{push 1} commands, and zero or
  more \akey{pop 1} commands, consistent with the uses of those
  commands in the SMT-LIB standard. Each \akey{check-sat} command may
  be preceded by a \akey{set-info :status} command that indicates the
  expected result of the \akey{check-sat} command.
\item Optionally, the script may contain an $\akey{exit}$ command as
  its last command.
\item The formulas in the script belong to the benchmark's logic, with
  any free symbols declared in the script.
\item All sorts declared with a $\akey{declare-sort}$ command must
  have zero arity.
\item Application track scripts may have $\akey{define-sort}$
  commands.
\item No other commands besides the ones just mentioned may be used.
\item Named formulas are not used in benchmark scripts.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Documents''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

@@

The main track competition uses a StarExec post-processor (named
``SMTCOMP2015") to accumulate the results.

>>>>

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.0, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB~v2 commands in
which:
%
\begin{enumerate}
\item In the main track, there may be a (single) \akey{set-option
  :print-success ...} command.  Note that {\tt success} outputs are
  ignored by the post-processor used by the
  competition.\footnote{SMT-LIB~2.0 requires that a solver produce a
    \texttt{success} answer after each \akey{set-logic},
    \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
    (among others), unless the option \akey{:print-success} is set to
    false.  Ignoring the \texttt{success} outputs allows for
    submitting fully SMT-LIB~2.0 compliant solvers without the need
    for a wrapper script, while still allowing entrants of previous
    competitions to run without changes.}
\item In the application track, the \akey{:print-success} option may
  not be disabled; the application track executor will send an initial
  $\akey{set-option :print-success true}$ command to the solver.
\item The (single) $\akey{set-logic}$ command setting the benchmark's
  logic is the first command after any $\akey{set-option}$ commands.
\item The script next optionally contains (any number of)
  $\akey{set-info}$ commands, which may be ignored by the
  solver. Benchmarks will likely have some of the following
  \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)},
  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}, and
  \akey{(set-info :status ...)}.
\item In the main track, there is exactly one $\akey{check-sat}$
  command, following possibly several $\akey{assert}$ commands.
\item In the application track, there are one or more \akey{check-sat}
  commands, each preceded by one or more \akey{assert} commands.
  There may also be zero or more \akey{push 1} commands, and zero or
  more \akey{pop 1} commands, consistent with the uses of those
  commands in the SMT-LIB standard. Each \akey{check-sat} command may
  be preceded by a \akey{set-info :status} command that indicates the
  expected result of the \akey{check-sat} command.
\item The script may optionally contain an $\akey{exit}$ command as
  its last command.  In the application track, this command must not
  be omitted.
\item The formulas in the script belong to the benchmark's logic, with
  any free symbols declared in the script.
\item All sorts declared with a $\akey{declare-sort}$ command must
  have zero arity.
\item Application track scripts may have $\akey{define-sort}$
  commands.
\item No other commands besides the ones just mentioned may be used.
\item Named formulas are not used in benchmark scripts.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Documents''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

@@

The main track competition uses a StarExec post-processor (named
``SMT-COMP 2015") to accumulate the results.
